MSDS6372Project1

### 2021-01-25 MSDS6372Project1.Rmd
update with LASSO seed

########################################
# Try LASSO variable selection #########
########################################
library(glmnet)
#Dummy code categorical predictor variables
x <- model.matrix(MSRP~.,train)[,-1]
y <- train$MSRP
cv.out=cv.glmnet(x,y,alpha=1) #alpha=1 performs LASSO
par(mfrow=c(1,1))
plot(cv.out)
# Look at the coefficient for best lambda
# coef(cv.out, cv.out$lambda.min)
# Compute the final lasso model
lasso.model = glmnet(x,y,alpha = 1,lambda = cv.out$lambda.min)

>>>>

########################################
# Try LASSO variable selection #########
########################################
library(glmnet)
#Dummy code categorical predictor variables
x <- model.matrix(MSRP~.,train)[,-1]
y <- train$MSRP
set.seed(123) # Need a seed number to keep same results for LASSO
cv.out=cv.glmnet(x,y,alpha=1) #alpha=1 performs LASSO
par(mfrow=c(1,1))
plot(cv.out)
# Look at the coefficient for best lambda
coefficients = coef(cv.out, cv.out$lambda.min)
head(coefficients)
# Compute the final lasso model
lasso.model = glmnet(x,y,alpha = 1,lambda = cv.out$lambda.min)
# Check assumptions
